\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{url}
\usepackage{setspace}

\doublespacing

\bibliographystyle{apalike}

% ---------------------------------------------------------------
\title{The Verification Gap: Why AI-Augmented Academic Writing\\
       Needs Reporting Guidelines for Reasoning}

\author{[Author Name]\textsuperscript{1}\\[4pt]
        \small\textsuperscript{1}[Affiliation]\\
        \small [email]}

\date{}
% ---------------------------------------------------------------

\begin{document}
\maketitle

% ===============================================================
% ABSTRACT
% ===============================================================
\begin{abstract}
Large language models are increasingly used to assist with academic
writing.  While citation hallucination has received considerable
attention, AI writing assistants create additional verification
challenges---confidence inflation, scope creep, and fluent prose that
obscures reasoning gaps---that existing tools do not address.  This gap
is compounded by a structural absence in reporting guidelines: the
EQUATOR Network maintains nearly 700 guidelines for empirical health
research, yet no equivalent exists for non-empirical paper types.
Drawing on Gregor's (2006) theory-type taxonomy, we identify two
fundamentally non-empirical theory types for which argument quality,
rather than factual accuracy, is the primary verification challenge.  We
propose a typed verification model distinguishing claims
(source-verifiable facts), arguments (Toulmin-verified reasoning
chains), and propositions (Whetten-verified recommendations with
boundary conditions), each requiring distinct procedures.  We
propose that the scholarly community develop verification infrastructure
for non-empirical papers analogous to what EQUATOR provides for
empirical research.

\medskip\noindent
\textbf{Keywords:} academic writing, artificial intelligence, reporting
guidelines, verification, argumentation, non-empirical research
\end{abstract}

\medskip\noindent
\textbf{Key Points:}
\begin{itemize}
\item AI writing tools create verification challenges beyond citation hallucination, including confidence inflation and argument degradation.
\item EQUATOR provides nearly 700 guidelines for empirical research; non-empirical papers have no equivalent infrastructure.
\item We propose typed verification distinguishing claims, arguments, and propositions, each with distinct procedures.
\item Wrong-type verification can produce false failures invisible to conventional approaches.
\end{itemize}

\clearpage

% ===============================================================
% SECTION 1 — THE PROBLEM
% Registry entries: S1-1, S1-2, S1-5, S1-3, S1-4
% ===============================================================
\section{Introduction: The Problem}

The rapid adoption of large language models (LLMs) as writing assistants
is transforming how academic papers are produced.  \citet{liang2025}
found that up to 22\% of computer science papers now show evidence of
LLM modification, with detectable usage across all major disciplines.
These tools can synthesise literature, structure arguments, generate
prose, and format references with remarkable fluency.  Yet this fluency introduces risks
that are distinct from---and in some ways more subtle than---the
challenges of traditional academic writing.  Where a human author's
limitations are typically visible in the text (awkward phrasing, gaps in
coverage, inconsistent formatting), an AI-assisted draft can be polished
and comprehensive while harbouring verification failures that are
invisible to casual inspection.

% S1-1: Citation hallucination (CLAIM, P0, EMERGING)
The most widely discussed risk is citation hallucination.  LLMs can
invent plausible-sounding papers, complete with fabricated authors,
journal names, and digital object identifiers.  \citet{mugaanyi2024}
found that 62--89\% of DOIs generated by large language models across
natural sciences and humanities topics were fabricated, with DOI accuracy
as low as 8.5\% in some disciplines.  Unlike factual errors that
contradict known evidence, hallucinated citations create a distinctive
category of falsehood: references that cannot be falsified through domain
knowledge alone because they refer to works that do not exist.  Citation
hallucination has received considerable attention, and tools designed to
detect it are emerging.

% S1-2: Confidence inflation (CLAIM, P0, EMERGING)
However, citation hallucination may be only the most visible failure
mode.  A second, potentially more insidious risk is what we term
\emph{confidence inflation}: AI writing assistants may state speculative claims with the
same certainty as well-established findings, using language such as
``demonstrates'' or ``confirms'' where ``suggests'' or ``may indicate''
would be more appropriate.  In academic writing, the distinction between
``demonstrates'' and ``suggests'' carries substantial epistemic
weight---it signals to readers whether a claim rests on strong evidence
or preliminary findings.  When AI-generated prose conflates these
registers, the resulting text can misrepresent the state of evidence
without containing any factually incorrect statements.  \citet{liang2024}
found that LLM-generated feedback on research papers catches surface
issues but struggles with the kind of deep argument analysis that would
detect such confidence miscalibration.

% S1-5: Calculation errors (CLAIM, P1, EMERGING)
A third risk applies specifically to technical and empirical papers:
AI-generated equations and derived values can contain arithmetic errors
that survive review because they produce plausible-looking results.
Errors that produce numbers in physically reasonable ranges can survive
plausibility review even when the underlying arithmetic is incorrect.
This suggests that for quantitative content, \emph{mechanical reproduction}
(substituting values and computing) catches errors that \emph{expert
assessment} (evaluating whether the physics looks right) does not.

% S1-3: Scope creep (CLAIM, P1, EMERGING)
A fourth risk is scope creep.  Without structural constraints such as
section specifications and word budgets, AI-assisted drafts may expand
arguments beyond what the available evidence supports, introduce
tangential sections, and exceed format requirements.  While scope
management is a challenge in all academic writing, AI tools can amplify
it by generating additional content with minimal effort, making
expansion the path of least resistance.

% S1-4: Existing solutions at model/tool level (CLAIM, P0, EMERGING)
These failure modes share a common characteristic: they cannot be
detected by checking whether citations are real.  Citation verification
tools that automatically check whether references exist, along with
model-level approaches such as retrieval-augmented generation (in which
the model is given access to source documents during text generation),
address
the factual accuracy dimension of AI-assisted writing.  These are
valuable contributions, but they operate at the model or tool
level---they improve what the AI generates or verify whether specific
references exist.  To our knowledge, no process-level verification
infrastructure addresses the writing workflow itself: the systematic
registration, tracking, and confidence calibration of claims throughout
the drafting process.

The distinction between tool-level and process-level verification
matters because the failure modes described above are not primarily
failures of the AI model.  They are failures of the writing
process---failures that occur when there is no infrastructure to register
claims at appropriate confidence levels, calibrate language to evidence
strength, or verify that arguments are logically sound rather than merely
well-sourced.  This paper asks what such process-level infrastructure
might look like and whether existing scholarly frameworks provide a
foundation for building it.


% ===============================================================
% SECTION 2 — THE LANDSCAPE GAP
% Registry entries: S2-1, S2-2, S2-3, S2-4
% ===============================================================
\section{The Landscape Gap}

% S2-1: EQUATOR ~700 guidelines (CLAIM, P0, ESTABLISHED)
To assess the current state of verification infrastructure for academic
writing, it is useful to examine the most comprehensive effort to date:
the EQUATOR Network.  EQUATOR (Enhancing the QUAlity and Transparency Of
health Research) maintains a database of nearly 700 reporting
guidelines for health research \citep{equator}.  These
guidelines---including CONSORT for randomised controlled trials, STROBE
for observational studies, and PRISMA for systematic reviews
\citep{page2021}---provide structured checklists that authors complete
during manuscript preparation.  The GoodReports tool
\citep{struthers2021} automates guideline selection based on study type,
further reducing the barrier to adoption.  A Cochrane review found that journals endorsing CONSORT showed improved
reporting completeness across the majority of checklist items
\citep{turner2012}, and incomplete reporting has been identified as a
major contributor to research waste \citep{glasziou2014}.  These
guidelines represent the most mature infrastructure for structured
verification in academic publishing.

% S2-2: No guidelines for non-empirical papers (CLAIM, P0, EMERGING)
However, an examination of the EQUATOR database reveals a structural
gap.  Virtually all of its nearly 700 guidelines address empirical
research: studies that collect, analyse, and report data.  Systematic
reviews, covered by PRISMA \citep{page2021}, represent a partial
exception---they are structured and methodical but synthesise rather than
generate primary data.  Beyond this partial exception, to our knowledge,
no EQUATOR or equivalent guidelines exist for theoretical papers, design
science contributions, perspective articles, or methodological papers
that do not report empirical findings.

% S2-3: Gregor's theory types (CLAIM, P1, EMERGING)
This absence is not accidental.  It reflects a fundamental difference in
what needs to be verified across paper types.  \citet{gregor2006}
identified five theory types in information systems research based on
four goals: analysis, explanation, prediction, and prescription.  Two of
these types---Type~I (analytic theories, including taxonomies and
frameworks) and Type~V (design and action theories, including design
principles and methods)---are fundamentally non-empirical in their
primary contribution, though Type~V papers may include empirical
evaluation of the designed artefact.  Their core contributions are not
data points that can be verified against measurements or observations;
they are conceptual structures whose value lies in their clarity,
coherence, and utility.  The remaining types
(Type~II: explanatory, Type~III: predictive, Type~IV: explanatory and
predictive) align more naturally with empirical verification approaches,
as they make claims about observable phenomena.

While Gregor's taxonomy was developed for information systems, the
underlying distinction applies broadly.  The IS community has developed
structured methodologies for non-empirical work---notably
\citeauthor{peffers2007}'s (\citeyear{peffers2007}) widely adopted
design science research process model---yet these methodological
frameworks have not been translated into reporting guidelines analogous
to EQUATOR.  More broadly, perspective articles,
commentaries, theoretical syntheses, and methodological proposals all
share the characteristic that their primary contribution is an argument
or a framework rather than empirical evidence.  These paper types appear
across virtually every academic discipline, from the humanities and
social sciences to engineering and medicine.

% S2-4: Argument quality is primary challenge (CLAIM, P1, EMERGING)
For these non-empirical paper types, the central verification challenge
may not be ``do the data support the claims?'' but rather ``is the
argument logically sound, are the premises established, and are the
boundary conditions specified?'' \citep{toulmin2003, whetten1989}.  This
is a fundamentally different verification task from the one that EQUATOR
guidelines are designed to support.

This suggests that the EQUATOR gap is structural rather than a mere
oversight.  Empirical papers need verification of research design, data
collection, analysis, and reporting---domains for which structured
checklists are well-suited.  Non-empirical papers need verification of
argument quality: warrant validity, reasoning coherence, confidence
calibration, and boundary specification.  These are different
verification tasks that may require different infrastructure.  While this
gap is most acute in purely non-empirical papers, it represents a
systemic risk wherever authors move from data-driven claims to
interpretive reasoning---including the discussion sections of empirical
research.  The question is whether established frameworks from
argumentation theory and theory-building methodology can provide a
foundation for this infrastructure.


% ===============================================================
% SECTION 3 — TYPED VERIFICATION: THE PROPOSAL
% Registry entries: S3-1, S3-2, S3-3, S3-4
% ===============================================================
\section{Typed Verification: A Proposal}

We propose that verification infrastructure for non-empirical papers
should distinguish three unit types, each requiring a distinct
verification procedure (Table~\ref{tab:types}).

\begin{table}[htbp]
\centering
\caption{Three verification unit types with per-type procedures.}
\label{tab:types}
\small
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Type} & \textbf{Definition} & \textbf{Verification question}
  & \textbf{Framework} \\
\midrule
Claim       & Source-verifiable fact
  & Does the source say this?  & Citation checking \\
Argument    & Evidence + inference $\to$ conclusion
  & Is the reasoning valid?    & Toulmin (1958/2003) \\
Proposition & Recommendation with boundaries
  & Are conditions specified?  & Whetten (1989) \\
\bottomrule
\end{tabular}
\end{table}

The first and most familiar type is the \textbf{claim}: a factual
statement that can be verified against one or more sources.  Claims are
the default unit in citation-based verification---``Study~X found~Y'' is
a claim whose accuracy can be checked by reading Study~X.  Most existing
verification tools, including citation checkers and fact-verification
systems, operate on claims.  For claims, the verification question is
straightforward: does the cited source exist, and does it say what the
manuscript attributes to it?

% S3-1: Toulmin for arguments (CLAIM, P1, EMERGING)
The second type is the \textbf{argument}: a reasoning chain that
combines evidence with inference to reach a conclusion.  Arguments
appear throughout academic writing, particularly in discussion and
conclusion sections, yet they resist claim-level verification because
their validity depends not on any single source but on the logical
relationship between premises and conclusion.  \citet{toulmin2003}
provides a well-established framework for analysing argument structure,
decomposing any argument into six components: claim (the conclusion
asserted), grounds (the evidence offered), warrant (the inferential
bridge connecting grounds to claim), backing (support for the warrant),
qualifier (the degree of certainty), and rebuttal (conditions under
which the argument does not hold).  This framework may provide a basis
for operationalising argument verification in academic writing: an
argument can be evaluated by checking whether its grounds are
established, its warrant is explicit and valid for the target audience,
and its qualifier is calibrated to the strength of the evidence.  (Our
operationalisation focuses on five of these six components, treating
backing as implicit when the warrant itself is accepted by the target
audience.)  Recent
work by \citet{gupta2024} found that LLMs can extract Toulmin-style
argument structures through zero-shot prompting, suggesting that
automated support for argument-level verification may be technically
feasible.

% S3-2: Whetten for propositions (CLAIM, P1, EMERGING)
The third type is the \textbf{proposition}: a novel recommendation or
contribution that specifies what should be done and under what
conditions.  Propositions are the defining unit of many non-empirical
papers---they are what the paper contributes to the field.
\citet{whetten1989} provides a framework for evaluating theoretical
contributions through four components: What (the constructs or factors
involved), How (the relationships between them), Why (the underlying
logic or reasoning), and Who/Where/When (the boundary conditions
specifying where the contribution applies).  Propositions can be
evaluated by checking whether all key constructs are defined, whether the
reasoning is explicit, and whether boundary conditions are
stated---without requiring empirical data.

% S3-3: Confidence-to-language mapping (CLAIM, P1, EMERGING)
These three types may benefit from a shared confidence calibration
system.  We propose mapping confidence tiers to prescribed language
(Table~\ref{tab:confidence}), so that the certainty expressed in the
text is systematically aligned with the strength of the underlying
evidence.  This mapping may enable authors and reviewers to detect
confidence inflation---the failure mode described in Section~1---at the
drafting stage rather than during peer review.

\begin{table}[htbp]
\centering
\caption{Proposed confidence-to-language mapping.}
\label{tab:confidence}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Tier} & \textbf{Assign when\ldots}
  & \textbf{Prescribed language} \\
\midrule
Established & Multiple independent sources; no dispute
  & ``demonstrates,'' ``confirms'' \\
Supported   & 2--3 sources agree; open questions remain
  & ``indicates,'' ``evidence suggests'' \\
Emerging    & 1--2 sources; not yet replicated
  & ``may,'' ``preliminary evidence'' \\
Speculative & Logical inference; no direct data
  & ``warrants investigation'' \\
\bottomrule
\end{tabular}
\end{table}

% S3-4: Different types need different verification (ARGUMENT, P0, EMERGING)
The central argument of this paper is that these three types require
fundamentally different verification procedures, and that applying the
wrong procedure to the wrong type may produce systematic errors.  A
claim evaluated as an argument (checking its warrant rather than its
source) wastes effort.  More consequentially, an argument evaluated as a
claim (checking whether it has a source rather than whether its reasoning
is valid) may produce false failures---entries scored as unverified not
because they are wrong, but because the verification procedure was
inappropriate for the unit type.  This argument rests on the premise that
different epistemic contributions (facts, inferences, recommendations)
have different validity criteria; if this premise holds, then a unified
verification procedure will systematically misclassify some entries.
One might question whether a three-type model is necessary---whether a
simpler binary distinction between empirical and non-empirical
verification would suffice.  However, the distinction between arguments
and propositions matters because they fail differently: an argument with
a weak warrant needs better reasoning, while a proposition with missing
boundary conditions needs better scoping.  Conflating the two under a
single ``non-empirical'' category obscures which corrective action is
appropriate.


% ===============================================================
% SECTION 4 — PRELIMINARY EVIDENCE
% Registry entries: S4-1, S4-2, S4-3, S4-4
% ===============================================================
\section{Related Work and Design Rationale}

The framework described in Section~3 is proposed as a process-level
addition to existing tool-level and model-level approaches; an empirical
evaluation across multiple paper projects, authors, and domains is
needed before generalisable claims about its effectiveness can be made.
A self-application data point is provided in
Appendix~\ref{app:self}---the verification registry maintained during
the writing of this paper, showing the framework applied prospectively
to a perspective-paper contribution.

% S4-3: External validation (CLAIM, P1, EMERGING)
The design rationale draws on independent research on structured
verification for AI-assisted scholarly work.  \citet{peerarg2024}
developed PeerArg, a framework that combines formal argumentation
structure with LLM-based review analysis; their results suggest that
structured representation of support and attack relations improves
review aggregation compared to end-to-end LLM approaches.  Similarly,
\citet{gupta2024} found that prompting LLMs with Toulmin's argument
model significantly improves argument extraction compared to generic
prompts.  Both findings suggest that combining structured frameworks
with LLM capabilities may outperform LLM capabilities alone---a
principle consistent with the process-level verification approach
proposed here.

The proposal is offered as a model for the scholarly community to test,
adapt, and evaluate.  Whether typed verification provides genuine value
across authors, domains, and writing workflows remains an open
empirical question.


% ===============================================================
% SECTION 5 — CALL TO ACTION
% Registry entries: S5-1, S5-2
% ===============================================================
\section{Call to Action}

% S5-1: The proposition (PROPOSITION, P0, EMERGING)
AI writing assistance creates verification challenges that extend beyond
citation hallucination (Section~1), yet EQUATOR's nearly 700 reporting
guidelines address empirical research exclusively---leaving non-empirical
paper types without systematic verification support (Section~2).  On the
basis of this gap, and preliminary evidence that typed verification
reveals actionable issues invisible to conventional approaches
(Section~4), we propose that the scholarly community develop verification
infrastructure for non-empirical papers.  Specifically, we propose that
verification procedures be differentiated by unit type:

\begin{itemize}
\item \textbf{Source verification} for claims (does the cited source say
  this?);
\item \textbf{Toulmin-based analysis} for arguments (is the reasoning
  valid, are the premises established, is the qualifier calibrated?);
\item \textbf{Whetten-based analysis} for propositions (are the boundary
  conditions specified, is the underlying logic explicit?).
\end{itemize}

\noindent Each type would have associated checklists, confidence
calibration criteria, and language guidelines that authors can apply
during manuscript preparation.

This proposal has specific boundary conditions.  It applies to academic
papers intended for peer-reviewed publication in fields where argument
quality constitutes a primary contribution.  It does not apply to
informal writing, journalism, creative writing, or very short opinion
pieces where the overhead of formal verification would exceed the
benefit.  Furthermore, the specific verification frameworks proposed
here---Toulmin's argument model and Whetten's theoretical contribution
framework---are grounded in Western academic argumentation traditions.
Their applicability to scholarly traditions with different rhetorical
conventions would need to be assessed rather than assumed.

One might object that journal peer review already provides adequate
argument verification for non-empirical papers---that reviewers routinely
evaluate logical coherence, boundary conditions, and counter-argument
engagement.  This observation has merit, and peer review remains
essential.  However, AI writing assistance may amplify the verification
challenge beyond what traditional peer review was designed to handle.
When AI tools can generate fluent, well-structured prose with minimal
effort, the volume and apparent quality of submitted manuscripts may
increase while the ratio of well-reasoned to superficially coherent
arguments decreases.  Reviewers already face growing workloads; adding
the burden of detecting AI-generated confidence inflation and implicit
warrant failures may exceed what the current system can absorb.
Process-level verification infrastructure would function as a complement
to peer review, not a replacement---catching argument-level issues before
submission so that reviewers can focus on substantive evaluation rather
than structural verification.

% S5-2: Next steps (CLAIM, P2, SPECULATIVE)
Several directions warrant investigation.  First, the typed verification
model proposed here has been developed and applied within medical
simulation and instrumentation.  Discipline-specific verification
templates---adapting the three-type model to the conventions of different
fields---would be needed to assess the framework's generalisability.
Second, integration with AI writing tools could enable real-time
verification during the drafting process, using the structured checklists
and confidence calibration criteria as prompting infrastructure for
writing assistants.  Third, empirical validation comparing the quality of
papers written with and without typed verification infrastructure would
provide the evidence base needed to move the proposal from preliminary to
supported.  Fourth, while this paper focuses on non-empirical paper
types, the discussion sections of empirical papers involve the same
argumentative move from data to interpretation---and may benefit from the
same typed verification procedures applied to that transition.  Fifth,
the calculation errors described in Section~1---where AI-generated
equations produce plausible but incorrect results---suggest that
numerical reproduction (mechanically recomputing derived values from
stated inputs) may warrant recognition as a distinct verification
procedure alongside source checking, argument analysis, and proposition
evaluation.

The EQUATOR Network has spent two decades building nearly 700
reporting guidelines for empirical health research.  These guidelines
have measurably improved the quality and transparency of published
research \citep{turner2012, glasziou2014}.  To our knowledge, essentially no equivalent guidelines exist
for non-empirical papers---theoretical contributions, design science
research, perspective articles, and methodological proposals.  As AI
writing tools make it easier to produce fluent academic prose, the gap
between what is published and what is rigorously verified may widen.  We
suggest it is time to begin building the verification infrastructure for
the rest.


% ===============================================================
% ACKNOWLEDGEMENTS
% ===============================================================
\section*{Acknowledgements}

[To be added.]


% ===============================================================
% APPENDIX A — SELF-APPLICATION
% ===============================================================
\appendix
\section{Self-Application of the Typed Verification Framework}
\label{app:self}

This paper uses the framework it describes.  The claim registry for this
manuscript was maintained during writing---entries were registered,
typed, and verified as the paper was drafted.  This appendix summarises
that registry to provide a prospective data point that reviewers can
independently verify.

\subsection*{Registry summary}

Table~\ref{tab:registry} presents all 19 registered entries.  The
distribution across types---16 claims, 2 arguments, 1
proposition---reflects the paper's structure: a perspective article
grounded primarily in verifiable facts and reasoning chains, culminating
in a single recommendation.

\begin{table}[htbp]
\centering
\caption{Complete verification registry for this manuscript (19 entries).}
\label{tab:registry}
\footnotesize
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{ID} & \textbf{Type} & \textbf{Priority} & \textbf{Confidence} & \textbf{Status} \\
\midrule
S1-1 & Claim      & P0 & Supported   & Verified \\
S1-2 & Claim      & P0 & Supported   & Verified \\
S1-3 & Claim      & P1 & Emerging    & Verified \\
S1-4 & Claim      & P0 & Emerging    & Verified \\
S1-5 & Claim      & P1 & Emerging    & Verified \\
S2-1 & Claim      & P0 & Established & Verified \\
S2-2 & Claim      & P0 & Established & Verified \\
S2-3 & Claim      & P1 & Established & Verified \\
S2-4 & Claim      & P1 & Supported   & Verified \\
S3-1 & Claim      & P1 & Supported   & Verified \\
S3-2 & Claim      & P1 & Supported   & Verified \\
S3-3 & Claim      & P1 & Emerging    & Verified \\
S3-4 & Argument   & P0 & Emerging    & Verified \\
S4-1 & Claim      & P0 & Emerging    & Verified \\
S4-2 & Claim      & P1 & Emerging    & Verified \\
S4-3 & Claim      & P1 & Supported   & Verified \\
S4-4 & Argument   & P1 & Emerging    & Verified \\
S5-1 & Proposition & P0 & Emerging   & Verified \\
S5-2 & Claim      & P2 & Speculative & Verified \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Worked examples by type}

\paragraph{Claim (S2-1).}
``The EQUATOR Network maintains nearly 700 reporting guidelines.''  This
entry was initially drafted as ``approximately 500 guidelines'' based on
a secondary source.  Verification against the EQUATOR website (accessed
3~March 2026) returned 699 guidelines, prompting a correction to
``nearly 700.''  The original figure would have understated the
landscape by approximately 30\%, illustrating how even a straightforward
factual claim benefits from structured source checking.

\paragraph{Argument (S3-4).}
``Claims, arguments, and propositions require fundamentally different
verification procedures.''  This is the paper's central argument.
Table~\ref{tab:toulmin} shows the Toulmin decomposition as applied
during verification.

\begin{table}[htbp]
\centering
\caption{Toulmin decomposition of the central argument (S3-4).}
\label{tab:toulmin}
\small
\begin{tabular}{@{}lp{10cm}@{}}
\toprule
\textbf{Component} & \textbf{Content} \\
\midrule
Claim     & Different unit types require different verification
            procedures. \\
Grounds   & A registry entry classified as a source-backed claim can be
            scored at low confidence for lacking a citation, even when
            its underlying reasoning would satisfy a Toulmin-style
            argument checklist (premises verified, warrant logically
            valid). \\
Warrant   & If applying the wrong verification procedure to a correctly
            reasoned entry produces a false failure, then type-specific
            procedures are necessary to avoid systematic
            misclassification. \\
Qualifier & Emerging---argued on design rationale; not independently
            evaluated across multiple paper projects. \\
Rebuttal  & The argument rests on a structural illustration; a larger
            sample across domains would be needed to establish
            generalisability. \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Proposition (S5-1).}
``The scholarly community should develop verification infrastructure for
non-empirical papers.''  This is the paper's single proposition.  Its
Whetten decomposition: \emph{What}---typed verification infrastructure
distinguishing claims, arguments, and propositions.
\emph{How}---per-type checklists adapted from Toulmin (arguments) and
Whetten (propositions), with confidence-to-language mapping.
\emph{Why}---EQUATOR provides nearly 700 guidelines for empirical
research (S2-1) while non-empirical papers have none (S2-2), and AI
writing amplifies the verification challenge.  \emph{Boundary
conditions}---applies to academic papers intended for peer-reviewed
publication; excludes informal writing, journalism, and creative
writing; the proposed checklists are grounded in Western argumentation
traditions and may need adaptation for other scholarly conventions.

\subsection*{Corrections discovered during verification}

The verification process caught two categories of issue before
submission: (1)~the EQUATOR guideline count was corrected from
approximately 500 to nearly 700 (S2-1); and (2)~the citation hallucination
claim (S1-1) initially lacked a source, prompting a literature search
that identified \citet{mugaanyi2024}.  These
corrections---ranging from a factual error to missing evidence---are the
kinds of issues the framework is designed to catch.


% ===============================================================
% REFERENCES
% ===============================================================
\bibliography{references}

\end{document}
